Type Refinements for the Working Class

### 2015-11-15 paper.tex
More fixing up of the internal judgments to support families of judgments

  A \emph{global internal judgment} is a section
  $\Of{J}{\int_\Upsilon{\Omega^{\mathbbold{1}}}(\Upsilon)}\cong
  \IMode{\int_\Upsilon\Hom{\mathbb{J}}{\Yoneda{\Upsilon}}{\Omega}}$, which can
  be externalized as a judgment $\Of{\Embed{J}}{\mathbb{J}}$ whose derivations
  at $\Upsilon$ are the arrows
  $\Of{\phi}{\Hom{\mathbb{J}}{\Yoneda{\Upsilon}}{\mathbbold{1}}}$ such that the
  following diagram commutes:

  \[
    \begin{tikzcd}
      \IMode{\Yoneda{\Upsilon}}
        \arrow[r, dashed, "\OMode{\phi}"]
        \arrow[rd, "\IMode{J_\Upsilon}"']
      & \IMode{\mathbbold{1}} \arrow[d, "\IMode{\mathbf{true}}"] \\
      & \IMode{\Omega}
    \end{tikzcd}
  \]

  In most cases, we will say something like ``To know $\mathcal{J}$ is to have
  a judgment $\mathcal{J'}$'' rather than appealing directly to the subobject
  classifier.
\end{definition}

@@

 \begin{remark}
   Formally, the evaluation relation is given in our logical framework by a
   global internal judgment $\Of{\Downarrow_\tau}{\int_\SCtx
   \Omega^{\Exprs_\tau\times\Values_\tau\times\NaturalsPsh}}$, where
   $\NaturalsPsh$ is the constant presheaf $\MapsTo{\Upsilon}{\Naturals}$.
   Then, we know $\EvalN{\Upsilon}{\tau}{n}{M}{N}$ just when the
   externalization $\Embed{\Downarrow_\tau}(M,N,n)$ is evident at $\Upsilon$.
 \end{remark}

>>>>

  A \emph{global internal (family of) judgments} is a section
  $\Of{J}{\int_\SCtx {\Omega^{\mathcal{J}}}}\cong
  \IMode{\int_\Upsilon\Hom{\mathbb{J}}{\Yoneda{\Upsilon}\times\mathcal{J}}{\Omega}}$,
  which can be externalized as a ``total'' judgment $\Of{\Embed{J}}{\mathbb{J}}$
  for whose derivations at $\Upsilon$ are the arrows
  $\Of{\phi}{\Hom{\mathbb{J}}{\Yoneda{\Upsilon}}{\mathbbold{1}\times\mathcal{J}}}$
  such that the following diagram commutes:
  \[
    \begin{tikzcd}[cramped,sep=huge]
      \IMode{\Yoneda{\Upsilon}}
        \arrow[r, dashed, "\OMode{\phi}"]
        \arrow[rd, "\IMode{J_\Upsilon\Pair{1}{\pi_2\circ\phi}}"']
      & \IMode{\mathbbold{1}\times\mathcal{J}} \arrow[d, "\IMode{\mathbf{true}\circ\pi_1}"] \\
      & \IMode{\Omega}
    \end{tikzcd}
  \]

  Then, to say $\IMode{\Upsilon}\parallel\Embed{J}(E)$ where
  $\Member{E}{\mathcal{J}(\Upsilon)}$ is to assert that we have evidence
  $\Member{F}{\Embed{J}(\Upsilon)}$ such that $\IsEq{\pi_2(F)}{E}$.

  When asserting the existence of an internal judgment, in most cases we will
  say something like ``To know $\mathcal{J}$ is to have a judgment
  $\mathcal{J'}$'' rather than appealing directly to the subobject classifier.
\end{definition}

@@

 \begin{remark}
   Formally, the evaluation relation is given in our logical framework by a
   global internal judgment $\Of{\Downarrow_\tau}{\int_\SCtx
   \Omega^{\Exprs_\tau\times\Values_\tau\times\NaturalsPsh}}$, where
   $\NaturalsPsh$ is the constant presheaf $\MapsTo{\Upsilon}{\Naturals}$.
 \end{remark}
